Supervised Learning for Psychological Attention to High School Students

### 2020-11-16 article/article.tex

\section{Methodology}\label{sec:meth}

>>>>

\section{Methodology}\label{sec:meth}
All the code developed for this work was implemented in Julia 1.5.3. and 
can be found in the authors'
\href{https://github.com/juanscr/ai-works}{GitHub repository}.

\subsection{Survey}
The used survey for extracting data was initially designed for developing
a Fuzzy inference expert system, but the data was labeled according to
unsupervised clustering techniques, obtaining 2 clusters through the subtractive
algorithm \parencite{chiu1994} and then sharpened using Fuzzy-C-Means 
\parencite{dunn1973}. The data has 6 variables and 113 observations.

\subsection{Support Vector Machines}
We refer to \textcite{burges1998} for the theoretical background on Support
Vector Machines (SVMs).

\subsection{Decision Trees}
We refer to

\subsection{Neural Networks}
We refer to \textcite{aggarwal2018} for the formulation of the Neural Netwok 
(NN) learning machine and the details of its implementation, such as the 
backpropagation algorithm for training and the bias correction. The NN was
implemented by the authors, including the bias correction and the
